A Motion Blur Resilient Fiducial For Quadcopter Imaging

### 2014-06-09 WACV/paper.tex
Done changes suggested by Prof. Sharat.

% Pages are numbered in submission mode, and unnumbered in camera-ready
\ifwacvfinal\pagestyle{empty}\fi
\begin{document}
\title{A Motion Blur Resilient Fiducial Marker For Quadcopter Imaging}
\maketitle

@@

  Fiducial markers are commonly placed in environments to provide a
  uniquely identifiable object in the scene.  In quadcopter
  applications, these fiducials are often used to evaluate planning
  algorithms given that ground truth positions can be
  detected from the quadcopter's camera.

  Low cost quadcopters, however, are subject to quick and unstable
  motions that can cause significant motion blur that severely affects
  the detection rate of existing fiducial markers. This problem
  motivated us to design a fiducial that is robust to motion blur. Our
  proposed design uses concentric circles with the observation that
  the direction perpendicular to the motion blur direction will be
  relatively unaffected by the blur. As a result, an appropriate
  fiducial code orthogonal to the blur direction can be
  recognized. Since the direction of motion blur is unknown, the
  circular design is good for all motion blur directions. We describe
  the design of binary fiducial markers, and also a detection
  algorithm.  We show that our marker can significantly outperform
  existing fiducial markers in scenes captured with a quadcopter.

@@

The recent availability of low-cost quadcopters has helped  fuel
significant efforts in research focused on unmanned aerial
vehicles. Navigation and planning
of these vehicles is typically~\cite{Davison:2007,Engel12,Engel13}
performed using onboard inertial sensors and/or vision based modules
that uses visual cues in the real world. However, to evaluate the
effectiveness of navigation methods, one or more fiducial markers are commonly
placed~\cite{Bosnak:2012,Lim09,Klopschitz:2007}
 in the environment to provide additional information that
serves for ground-truth positional measurements.

In order to be effective, fiducial markers (or simply, fiducials) need
to be easily detected in the scene. A variety of fiducial markers have
been proposed~\cite{NaimarkF02,ARToolkit02,Fiala05,Pitag13,runetag11}
in the literature.  These take the form of binary codes arranged into
rectangular grids~\cite{ARToolkit02,Fiala05} or other geometric
primitives arranged in predefined spatial
patterns~\cite{NaimarkF02,Pitag13,runetag11}.  Figure \ref{fig:teaser}
shows the popular ARTag \cite{Fiala05} fiducial as possibly seen from
a quadcopter. A problem for existing fiducials is that low-cost
quadcopters often exhibit very quick and erratic physical movements
that result in motion blur in the quadcopter's onboard camera. This
motion blur has an adverse effect on the recognition of fiducial
markers. This can be seen in Figure \ref{fig:teaser}--(b) where the
ARTag fiducial cannot be recognized due to motion blur. This is not
too surprising as most existing fiducials are not designed to handle
motion blur.

@@

The remainder of this paper is organized as follows.  Section~2 gives
an overview of related work in fiducials, as well as the related
problem of tracking. Section~3 motivates our fiducial design by
analysing the performance of existing codes under motion blur, and
describes our detection algorithm. Section~4 shows several
experiments using quadcopter imagery. This is followed by a discussion
and a summary in Section~5 and Section~6 respectively.

@@

Our work is related to two areas: fiducial markers and object tracking. We
briefly discuss work done in both areas.

\textbf{Fiducials:}~Figure~\ref{fig:previous_work} shows a few
examples of existing fiducial markers.  Many designs use a two
dimensional barcode inside a rectangular grid. One example of such a
fiducial is from the ARToolkit~\cite{ARToolkit02}, a well known
toolkit used in many augmented reality (AR) applications. Kato and
Billinghurst~\cite{kato-artoolkit} first demonstrated the use of
ARToolkit in various augmented-reality-based applications.

\begin{figure}[b!]
\centering
 \begin{subfigure}[b]{0.23\linewidth}
  \centering
  \includegraphics[width=0.8\linewidth]{images/intersense.jpg}
  Circular Data Matrix~\cite{NaimarkF02}
 \end{subfigure}\quad
 \begin{subfigure}[b]{0.14\linewidth}
 \centering
  \includegraphics[width=\linewidth]{images/pattKanji.pdf}
  ARToolkit~\cite{ARToolkit02}
 \end{subfigure}\quad
 \begin{subfigure}[b]{0.12\linewidth}
  \centering
  \includegraphics[width=\linewidth]{images/ARtag.jpg}
  ARTag\quad~\cite{Fiala05}
 \end{subfigure}\quad
 \begin{subfigure}[b]{0.12\linewidth}
  \centering
  \includegraphics[width=\linewidth]{images/pifiducial.jpg}
  PiTag\quad~\cite{Pitag13}
 \end{subfigure}\quad
 \begin{subfigure}[b]{0.14\linewidth}
  \centering
  \includegraphics[width=\linewidth]{images/our_fiducial}
  Our Fiducial
 \end{subfigure}
 \caption{Prior fiducial markers and our proposal.  While
 each code has its pros and cons depending on the environment, no
 prior code is expressly designed to be recognized under motion blur.}
 \label{fig:previous_work}
\end{figure}

@@

%Zhang et al.\cite{Zhang:2002} and Claus et al. \cite{ClausF04} have done
%quite comprehensive comparative study of various fiducial marker systems with
%respect to processing time, recognition rate and accuracy with
%respect to viewing angle and distance.

@@

%To evaluate the ARTag and PiTag under blur, 
For controlled study, we simulate the appearance of the ARTag and PiTag
markers by scaling the tags to 150$\times$150 pixels.
Both fiducials are then blurred using linear motion blur at various
orientations with different  blur scales. The blur motion ranged from 15 to 50
in magnitude (measured in pixels), representing small to significant motion
blur. Figure~\ref{fig:artag_pitag} shows the visual appearance of the blurred
tags. We then try to detect the markers using the ALVAR library~\cite{alvar} and
PiTag library~\cite{ros_pitag}. The table in %the right side of
Figure~\ref{fig:artag_pitag} shows the recognition rate (in
percentage) of the two
fiducial markers at various blur scales over all  orientations.
As we can see, the PiTag performance quickly diminishes under small amounts of
blur, while at 35 units, the ARTag's recognition rate drops to less than
20\%.

\begin{figure}[t!]
\includegraphics[width=\linewidth]{images/artag_pitag.pdf}
%\captionof{figure}{Blurred ARTag and Pi--tag with various blur scales}
%\captionof{table}{Recognition rate of ARTag and Pi-tag fiducial marker atvarious blur scales}

@@

%\noindent Details of each of the steps are as follows:\\
\textbf{Gabor filter}~~A 2D Gabor filter is a Gaussian kernel function
modulated by a sinusoidal plane wave~\cite{Kruizinga:2002}. It is used to find
high gradient patches. In our case, it is used to detect portions
of the circular fiducials that were not affected by the blur.
We applied the Gabor filter in eight
different orientations ($\theta = 0, 45, 90, \ldots, 225, 270, 315$).  The
following parameters were used for creating each Gabor kernel: $\lambda$ (wavelength) $= 8$, $\gamma$
(aspect ratio) $= 0.5$, $\sigma$ (spread) $= 0.56\lambda$, $\psi$
(phase angle) $= 0$ (for real part), $\pi/2$ (for imaginary part).
Then $\ell^2$-norm of outputs along all orientations is calculated and finally
$\ell^2$-normalized image is thresholded with threshold set to $0.4$ (on scale of zero to
one).  For further details to the Gabor filter, see~\cite{Kruizinga:2002}.
%% MBS - is the Kruizinga filter resonable to cite?

@@

\textbf{Classification}~~As mentioned above, a small image patch
containing the intensity profile of the fiducial is used to identify
which of the many fiducials might be present and is represented by a
code.  We found that a training-based method using the k nearest
neighbor (k-NN) technique gave better results than trying to find
binary code directly by determining the presence (or absence) of ring
at particular positions in the image patch. This required
training-data which was easy to generate. A synthetic fiducial pattern
is blurred along 36 orientations (0, 10, 20, \ldots , 350) with blur
scale set to 40, and the intensity profile along the first principal
component from every output is taken as training data for that
fiducial pattern. Figure~\ref{fig:training_data} shows the process of
creating training data for fiducial with binary code ``01'' embedded
in it.  For a query image patch, we normalize the intensity range, and
then compare this information against the training data. The class
label from the closest top $K=5$ images in the training data is used
to label the patch.

\begin{figure}[h!]
\centering
  \includegraphics[width=0.95\linewidth]{images/training_data.pdf}
  \caption{Creating training data for the fiducial pattern with binary
  code ``01'': The synthetic pattern is blurred along various
  orientations and the intensity profile monitored and stored. The
  same process is used to create training data for all other fiducials.}
  \label{fig:training_data}
\end{figure}

@@

Our system has been tested on several image sequences captured from an
AR Drone quadcopter.  The drone was flown indoors looking at patterns
attached to various walls. Each image sequence contains frames of
different fiducials. Some sample outputs for each fiducial pattern
is shown in Figure~\ref{fig:out_outputs}. Our detection process takes
around 0.3 seconds which translates to slightly over three frames per
second.

@@

Our system has also been tested on images containing multiple fiducial
patterns in the same frame. Our algorithm can successfully detected
all fiducial patterns as well as correctly classified them as shown in
Figure \ref{fig:output_all}.

@@

\begin{table}[h!]
  \centering
  \begin{tabularx}{\linewidth}{|c|Y|}
    \cline{1-2}
    \footnotesize{Blur} & \footnotesize{Mean($\pm$std) error}  \\
    \footnotesize{angle} & \footnotesize{(in pixels)}  \\
    \cline{1-2}
    \footnotesize{0} & \footnotesize{1.33 $\pm$ 0.40}  \\
    \footnotesize{22} & \footnotesize{2.42 $\pm$ 1.05} \\
    \footnotesize{45} & \footnotesize{1.46 $\pm$ 0.65}  \\
    \footnotesize{67} & \footnotesize{2.39 $\pm$ 1.28}  \\
    \footnotesize{90} & \footnotesize{1.83 $\pm$ 0.25}  \\
    \cline{1-2}
  \end{tabularx}
    \caption{Center localization error.
      Error is computed for various blur angles over various scales.}
    \label{tab:blur_angle_center}
\end{table}

\begin{comment}
\begin{figure*}
\centering
\begin{tabular}{c|c}
\begin{subfigure}[b]{0.45\linewidth}
\centering
\includegraphics[width=\linewidth]{images/recognition_rate.pdf}
\caption{Comparison of recognition rate of fiducials}
\label{fig:recognition_rate}
\end{subfigure}
&
\begin{subfigure}[b]{0.25\linewidth}
\centering
\begin{tabularx}{\textwidth}{|c|Y|}
\cline{1-2}
\footnotesize{Blur} & \footnotesize{Mean($\pm$std) error}  \\
\footnotesize{angle} & \footnotesize{(in pixels)}  \\
\cline{1-2}
\footnotesize{0} & \footnotesize{1.33 $\pm$ 0.40}  \\
\footnotesize{22} & \footnotesize{2.42 $\pm$ 1.05} \\
\footnotesize{45} & \footnotesize{1.46 $\pm$ 0.65}  \\
\footnotesize{67} & \footnotesize{2.39 $\pm$ 1.28}  \\
\footnotesize{90} & \footnotesize{1.83 $\pm$ 0.25}  \\
\cline{1-2}
\end{tabularx}
\caption{Center localization error}
\label{tab:blur_angle_center}
\end{subfigure}
\end{tabular}
\caption{(a): Comparison of recognition rate of the ARTag and our fiducials on
blur simulated data at various blur scales. It can be seen that except for the
fiducial with binary code ``00'', our fiducial patterns are recognized all times.
(b): Table showing the mean error and standard deviation of the localized fiducial center
versus the ground truth.  Error is computed for various blur angles over
different blur scales.}
\label{fig:simulated_blur}
\end{figure*}
\end{comment}

@@

\begin{table}[t!]
  \centering
  \begin{tabularx}{\linewidth}{|c|Y|Y|Y|Y|}
    \cline{1-5}
    \multirow{2}{*}{Test \#} & {Number}
    &{Binary} &\multicolumn{2}{c|}{Recognition Rate (\%)} \\
    \cline{4-5} & {of frames}& {Code}& ARTag & Our Fiducial \\\cline{1-5}
    1 & 1205 & 00 &  65.6 & 86.5  \\ \cline{1-5}
    2 & 1047 & 01 &  61.9 & 94.1  \\ \cline{1-5}
    3 & 1102 & 10 &  62.4 & 92.74 \\ \cline{1-5}
    4 & 1081 & 11 &  60.3 & 93.54  \\ \cline{1-5}
  \end{tabularx}
  \caption{  \label{tab:recognition_accuracy}
Recognition rate of ARTag and propsosed fiducials on real
    data captured through AR Drone. Each row shows analysis of a test
    dataset captured for our fiducial with different binary codes embedded in it.
    Each dataset has around 1000 frames captured representing roughly two
    minutes of video.} 
\end{table}

@@

We also compare our approach with tracking designed for blurred input
scenes.  We have used four image sequences (consisting of around 1000
frames each). Each sequence contains different fiducials so that we
are able to contrast the performance of BLUT~\cite{Wu:2011} with the
proposed method.  From the images in the top rows of
Figure~\ref{fig:BLUT_compare_00} and Figure~\ref{fig:BLUT_compare_01},
we can see that BLUT is able to track the fiducial when the position
of fiducial does not change too much in successive frames. Also, it
can be seen that once BLUT loses track of the fiducial, it is not
able to recover. Since our approach detects the code in each frame,
large changes in the patterns position is not an issue.  Some of our
detection results are also shown in Figure~\ref{fig:BLUT_compare_00}
and Figure~\ref{fig:BLUT_compare_01}.

@@

\begin{figure*}
\begin{subfigure}[b]{.19\textwidth}
\includegraphics[width=\linewidth]{images/BLUT_output_00/2.jpg}
\end{subfigure}
\begin{subfigure}[b]{.19\textwidth}
\includegraphics[width=\linewidth]{images/BLUT_output_00/3.jpg}
\end{subfigure}
\begin{subfigure}[b]{.19\textwidth}
\includegraphics[width=\linewidth]{images/BLUT_output_00/4.jpg}
\end{subfigure}
\begin{subfigure}[b]{.19\textwidth}
\includegraphics[width=\linewidth]{images/BLUT_output_00/5.jpg}
\end{subfigure}
\begin{subfigure}[b]{.19\textwidth}
\includegraphics[width=\linewidth]{images/BLUT_output_00/6.jpg}
\end{subfigure}\\
\begin{subfigure}[b]{.19\textwidth}
\includegraphics[width=\linewidth]{images/BLUT_input_00/output2.jpg}
\end{subfigure}
\begin{subfigure}[b]{.19\textwidth}
\includegraphics[width=\linewidth]{images/BLUT_input_00/output3.jpg}
\end{subfigure}
\begin{subfigure}[b]{.19\textwidth}
\includegraphics[width=\linewidth]{images/BLUT_input_00/output4.jpg}
\end{subfigure}
\begin{subfigure}[b]{.19\textwidth}
\includegraphics[width=\linewidth]{images/BLUT_input_00/output5.jpg}
\end{subfigure}
\begin{subfigure}[b]{.19\textwidth}
\includegraphics[width=\linewidth]{images/BLUT_input_00/output6.jpg}
\end{subfigure}
\caption{\textbf{Top:} Output of BLUT~\cite{Wu:2011}. \textbf{Bottom:}
  Output of our algorithm on the same image 
  sequence. BLUT is able to track the fiducial till the third frame,
  but from the fourth frame onwards, BLUT loses track. In the first
  three frames, the size of the  bounding box is low, but in the fourth
  and fifth frame it is large, indicating a sudden forward movement
  of the quadcopter.} 
\label{fig:BLUT_compare_00}
\end{figure*}

\begin{figure*}
\begin{subfigure}[b]{.19\textwidth}
\includegraphics[width=\linewidth]{images/BLUT_output_01/11.jpg}
\end{subfigure}
\begin{subfigure}[b]{.19\textwidth}
\includegraphics[width=\linewidth]{images/BLUT_output_01/12.jpg}
\end{subfigure}
\begin{subfigure}[b]{.19\textwidth}
\includegraphics[width=\linewidth]{images/BLUT_output_01/13.jpg}
\end{subfigure}
\begin{subfigure}[b]{.19\textwidth}
\includegraphics[width=\linewidth]{images/BLUT_output_01/14.jpg}
\end{subfigure}
\begin{subfigure}[b]{.19\textwidth}
\includegraphics[width=\linewidth]{images/BLUT_output_01/15.jpg}
\end{subfigure}\\
\begin{subfigure}[b]{.19\textwidth}
\includegraphics[width=\linewidth]{images/BLUT_input_01/output11.jpg}
\end{subfigure}
\begin{subfigure}[b]{.19\textwidth}
\includegraphics[width=\linewidth]{images/BLUT_input_01/output12.jpg}
\end{subfigure}
\begin{subfigure}[b]{.19\textwidth}
\includegraphics[width=\linewidth]{images/BLUT_input_01/output13.jpg}
\end{subfigure}
\begin{subfigure}[b]{.19\textwidth}
\includegraphics[width=\linewidth]{images/BLUT_input_01/output14.jpg}
\end{subfigure}
\begin{subfigure}[b]{.19\textwidth}
\includegraphics[width=\linewidth]{images/BLUT_input_01/output15.jpg}
\end{subfigure}
\caption{{\bf Top:} Output of BLUT~\cite{Wu:2011} on a sequence containing
the ``01'' binary coded fiducial. {\bf Bottom:} Output of our
algorithm on the same image 
sequence. BLUT loses  track from the third frame onwards.}
\label{fig:BLUT_compare_01}
\end{figure*}

@@

In terms of numbers of fiducials, we are able to generate less markers
than ARTag. Many applications in robotics (e.g. quadcopter navigation)
may not require simultaneous use of a large number of fiducials.  Most
of the time, it is sufficient to have 4-6 different
fiducials. Nevertheless, we may be able to generate a larger number of
fiducials by using color backgrounds. This is an area of interest for
further investigation.

>>>>

% Pages are numbered in submission mode, and unnumbered in camera-ready
\ifwacvfinal\pagestyle{empty}\fi
\begin{document}
\title{A Motion Blur Resilient Fiducial For Quadcopter Imaging}
\maketitle

@@

  fiducials are commonly placed in environments to provide a
  uniquely identifiable object in the scene.  In quadcopter
  applications, these fiducials are often used to evaluate planning
  algorithms given that ground truth positions can be
  detected from the quadcopter's camera.

  Low cost quadcopters, however, are subject to quick and unstable
  motions that can cause significant motion blur that severely affects
  the detection rate of existing fiducials. This problem
  motivated us to design a fiducial that is robust to motion blur. Our
  proposed design uses concentric circles with the observation that
  the direction perpendicular to the motion blur direction will be
  relatively unaffected by the blur. As a result, an appropriate
  fiducial code orthogonal to the blur direction can be
  recognized. Since the direction of motion blur is unknown, the
  circular design is good for all motion blur directions. We describe
  the design of binary fiducials, and also a detection
  algorithm.  We show that our marker can significantly outperform
  existing fiducials in scenes captured with a quadcopter.

@@

The recent availability of low-cost quadcopters has helped  fuel
significant efforts in research focused on unmanned aerial
vehicles. Navigation and planning
of these vehicles is typically~\cite{Davison:2007,Engel12,Engel13}
performed using onboard inertial sensors and/or vision based modules
that uses visual cues in the real world. However, to evaluate the
effectiveness of navigation methods, one or more fiducials are commonly
placed~\cite{Bosnak:2012,Lim09,Klopschitz:2007}
 in the environment to provide additional information that
serves for ground-truth positional measurements.

In order to be effective, fiducials (or simply, fiducials) need
to be easily detected in the scene. A variety of fiducials have
been proposed~\cite{NaimarkF02,ARToolkit02,Fiala05,Pitag13,runetag11}
in the literature.  These take the form of binary codes arranged into
rectangular grids~\cite{ARToolkit02,Fiala05} or other geometric
primitives arranged in predefined spatial
patterns~\cite{NaimarkF02,Pitag13,runetag11}.  Figure \ref{fig:teaser}
shows the popular ARTag \cite{Fiala05} fiducial as possibly seen from
a quadcopter. A problem for existing fiducials is that low-cost
quadcopters often exhibit very quick and erratic physical movements
that result in motion blur in the quadcopter's onboard camera. This
motion blur has an adverse effect on the recognition of fiducial
markers. This can be seen in Figure \ref{fig:teaser}--(b) where the
ARTag fiducial cannot be recognized due to motion blur. This is not
too surprising as most existing fiducials are not designed to handle
motion blur.

@@

The remainder of this paper is organized as follows.  Section~2 gives
an overview of related work in fiducials, as well as the related
problem of tracking. Section~3 motivates our fiducial design by
analyzing the performance of existing codes under motion blur, and
describes our detection algorithm. Section~4 shows several
experiments using quadcopter imagery. This is followed by a discussion
and a summary in Section~5 and Section~6 respectively.

@@

Our work is related to two areas: fiducials and object tracking. We
briefly discuss work done in both areas.

\textbf{Fiducials:}~Figure~\ref{fig:previous_work} shows a few
examples of existing fiducials.  Many designs use a two
dimensional barcode inside a rectangular grid. One example of such a
fiducial is from the ARToolkit~\cite{ARToolkit02}, a well known
toolkit used in many augmented reality (AR) applications. Kato and
Billinghurst~\cite{kato-artoolkit} first demonstrated the use of
ARToolkit in various augmented-reality-based applications.

\begin{figure}[b!]
\centering
 \begin{subfigure}[b]{0.23\linewidth}
  \centering
  \includegraphics[width=0.8\linewidth]{images/intersense.jpg}
  Circular Data Matrix~\cite{NaimarkF02}
 \end{subfigure}\quad
 \begin{subfigure}[b]{0.14\linewidth}
 \centering
  \includegraphics[width=\linewidth]{images/pattKanji.pdf}
  ARToolkit~\cite{ARToolkit02}
 \end{subfigure}\quad
 \begin{subfigure}[b]{0.12\linewidth}
  \centering
  \includegraphics[width=\linewidth]{images/ARtag.jpg}
  ARTag\quad~\cite{Fiala05}
 \end{subfigure}\quad
 \begin{subfigure}[b]{0.12\linewidth}
  \centering
  \includegraphics[width=\linewidth]{images/pifiducial.jpg}
  PiTag\quad~\cite{Pitag13}
 \end{subfigure}\quad
 \begin{subfigure}[b]{0.14\linewidth}
  \centering
  \includegraphics[width=\linewidth]{images/our_fiducial}
  Our Fiducial
 \end{subfigure}
 \caption{Prior fiducials and our proposal.  While
 each code has its pros and cons depending on the environment, no
 prior code is expressly designed to be recognized under motion blur.}
 \label{fig:previous_work}
\end{figure}

@@

%Zhang et al.\cite{Zhang:2002} and Claus et al. \cite{ClausF04} have done
%quite comprehensive comparative study of various fiducial systems with
%respect to processing time, recognition rate and accuracy with
%respect to viewing angle and distance.

@@

%To evaluate the ARTag and PiTag under blur, 
For controlled study, we simulate the appearance of the ARTag and PiTag
markers by scaling the tags to 150$\times$150 pixels.
Both fiducials are then blurred using linear motion blur at various
orientations with different  blur scales. The blur motion ranged from 15 to 50
in magnitude (measured in pixels), representing small to significant motion
blur. Figure~\ref{fig:artag_pitag} shows the visual appearance of the blurred
tags. We then try to detect the markers using the ALVAR library~\cite{alvar} and
PiTag library~\cite{ros_pitag}. The table in %the right side of
Figure~\ref{fig:artag_pitag} shows the recognition rate (in
percentage) of the two
fiducials at various blur scales over all  orientations.
As we can see, the PiTag performance quickly diminishes under small amounts of
blur, while at 35 units, the ARTag's recognition rate drops to less than
20\%.

\begin{figure}[t!]
\includegraphics[width=\linewidth]{images/artag_pitag.pdf}
%\captionof{figure}{Blurred ARTag and Pi--tag with various blur scales}
%\captionof{table}{Recognition rate of ARTag and Pi-tag fiducial at various blur scales}

@@

%\noindent Details of each of the steps are as follows:\\
\textbf{Gabor filter}~~A 2D Gabor filter is a Gaussian kernel function
modulated by a sinusoidal plane wave~\cite{Kruizinga:2002}. It is used to find
high gradient patches. In our case, it is used to detect portions
of the circular fiducials that were not affected by the blur.
We applied the Gabor filter in eight
different orientations ($\theta = 0, 45, 90, \ldots, 225, 270, 315$).  The
following parameters were used for creating each Gabor kernel: $\lambda$ (wavelength) $= 8$, $\gamma$
(aspect ratio) $= 0.5$, $\sigma$ (spread) $= 0.56\lambda$, $\psi$
(phase angle) $= 0$ (for real part), $\pi/2$ (for imaginary part).
Then $\ell^2$-norm of outputs along all orientations is calculated and finally
$\ell^2$-normalized image is thresholded with threshold set to $0.4$ (on scale of zero to
one).  For further details to the Gabor filter, see~\cite{Kruizinga:2002}.
%% MBS - is the Kruizinga filter reasonable to cite?

@@

\textbf{Classification}~~As mentioned above, a small image patch
containing the intensity profile of the fiducial is used to identify
which of the many fiducials might be present and is represented by a
code.  We found that a training-based method using the k nearest
neighbor (k-NN) technique gave better results than trying to find
binary code directly by determining the presence (or absence) of ring
at particular positions in the image patch. This required
training-data which was easy to generate. A synthetic fiducial
is blurred along 36 orientations (0, 10, 20, \ldots , 350) with blur
scale set to 40, and the intensity profile along the first principal
component from every output is taken as training data for that
fiducial. Figure~\ref{fig:training_data} shows the process of
creating training data for fiducial with binary code ``01'' embedded
in it.  For a query image patch, we normalize the intensity range, and
then compare this information against the training data. The class
label from the closest top $K=5$ images in the training data is used
to label the patch.

\begin{figure}[h!]
\centering
  \includegraphics[width=0.95\linewidth]{images/training_data.pdf}
  \caption{Creating training data for the fiducial with binary
  code ``01'': The synthetic pattern is blurred along various
  orientations and the intensity profile monitored and stored. The
  same process is used to create training data for all other fiducials.}
  \label{fig:training_data}
\end{figure}

@@

Our system has been tested on several image sequences captured from an
AR Drone quadcopter.  The drone was flown indoors looking at patterns
attached to various walls. Each image sequence contains frames of
different fiducials. Some sample outputs for each fiducial
is shown in Figure~\ref{fig:out_outputs}. Our detection process takes
around 0.3 seconds which translates to slightly over three frames per
second.

@@

Our system has also been tested on images containing multiple fiducial
patterns in the same frame. Our algorithm can successfully detected
all fiducials as well as correctly classified them as shown in
Figure \ref{fig:output_all}.

@@

\begin{table}[h!]
  \centering
  \begin{tabularx}{0.6\linewidth}{|Y|Y|}
    \cline{1-2}
    \footnotesize{Blur} & \footnotesize{Mean($\pm$std) error}  \\
    \footnotesize{angle} & \footnotesize{(in pixels)}  \\
    \cline{1-2}
    \footnotesize{0} & \footnotesize{1.33 $\pm$ 0.40}  \\
    \footnotesize{22} & \footnotesize{2.42 $\pm$ 1.05} \\
    \footnotesize{45} & \footnotesize{1.46 $\pm$ 0.65}  \\
    \footnotesize{67} & \footnotesize{2.39 $\pm$ 1.28}  \\
    \footnotesize{90} & \footnotesize{1.83 $\pm$ 0.25}  \\
    \cline{1-2}
  \end{tabularx}
    \caption{Center localization error.
      Error is computed for various blur angles over various scales.}
    \label{tab:blur_angle_center}
\end{table}

\begin{comment}
\begin{figure*}
\centering
\begin{tabular}{c|c}
\begin{subfigure}[b]{0.45\linewidth}
\centering
\includegraphics[width=\linewidth]{images/recognition_rate.pdf}
\caption{Comparison of recognition rate of fiducials}
\label{fig:recognition_rate}
\end{subfigure}
&
\begin{subfigure}[b]{0.25\linewidth}
\centering
\begin{tabularx}{\textwidth}{|c|Y|}
\cline{1-2}
\footnotesize{Blur} & \footnotesize{Mean($\pm$std) error}  \\
\footnotesize{angle} & \footnotesize{(in pixels)}  \\
\cline{1-2}
\footnotesize{0} & \footnotesize{1.33 $\pm$ 0.40}  \\
\footnotesize{22} & \footnotesize{2.42 $\pm$ 1.05} \\
\footnotesize{45} & \footnotesize{1.46 $\pm$ 0.65}  \\
\footnotesize{67} & \footnotesize{2.39 $\pm$ 1.28}  \\
\footnotesize{90} & \footnotesize{1.83 $\pm$ 0.25}  \\
\cline{1-2}
\end{tabularx}
\caption{Center localization error}
\label{tab:blur_angle_center}
\end{subfigure}
\end{tabular}
\caption{(a): Comparison of recognition rate of the ARTag and our fiducials on
blur simulated data at various blur scales. It can be seen that except for the
fiducial with binary code ``00'', our fiducials are recognized all times.
(b): Table showing the mean error and standard deviation of the localized fiducial center
versus the ground truth.  Error is computed for various blur angles over
different blur scales.}
\label{fig:simulated_blur}
\end{figure*}
\end{comment}

@@

\begin{table}[t!]
  \centering
  \begin{tabularx}{\linewidth}{|c|Y|Y|Y|Y|}
    \cline{1-5}
    \multirow{2}{*}{Test \#} & {Number}
    &{Binary} &\multicolumn{2}{c|}{Recognition Rate (\%)} \\
    \cline{4-5} & {of frames}& {Code}& ARTag & Our Fiducial \\\cline{1-5}
    1 & 1205 & 00 &  65.6 & 86.5  \\ \cline{1-5}
    2 & 1047 & 01 &  61.9 & 94.1  \\ \cline{1-5}
    3 & 1102 & 10 &  62.4 & 92.74 \\ \cline{1-5}
    4 & 1081 & 11 &  60.3 & 93.54  \\ \cline{1-5}
  \end{tabularx}
  \caption{  \label{tab:recognition_accuracy}
Recognition rate of ARTag and proposed fiducials on real
    data captured through AR Drone. Each row shows analysis of a test
    dataset captured for our fiducial with different binary codes embedded in it.
    Each dataset has around 1000 frames captured representing roughly two
    minutes of video.} 
\end{table}

@@

We also compare our approach with tracking designed for blurred input
scenes.  We have used four image sequences (consisting of around 1000
frames each). Each sequence contains different fiducials so that we
are able to contrast the performance of BLUT~\cite{Wu:2011} with the
proposed method.  From the images in the top rows of
Figure~\ref{fig:BLUT_compare_00} and Figure~\ref{fig:BLUT_compare_01},
we can see that BLUT is able to track the fiducial when the position
of fiducial does not change too much in successive frames. Also, it
can be seen that once BLUT looses track of the fiducial, it is not
able to recover. Since our approach detects the code in each frame,
large changes in the patterns position is not an issue.  Some of our
detection results are also shown in Figure~\ref{fig:BLUT_compare_00}
and Figure~\ref{fig:BLUT_compare_01}.

@@

\begin{figure*}
\begin{subfigure}[b]{.19\textwidth}
\includegraphics[width=\linewidth]{images/BLUT_output_00/2.jpg}
\end{subfigure}
\begin{subfigure}[b]{.19\textwidth}
\includegraphics[width=\linewidth]{images/BLUT_output_00/3.jpg}
\end{subfigure}
\begin{subfigure}[b]{.19\textwidth}
\includegraphics[width=\linewidth]{images/BLUT_output_00/4.jpg}
\end{subfigure}
\begin{subfigure}[b]{.19\textwidth}
\includegraphics[width=\linewidth]{images/BLUT_output_00/5.jpg}
\end{subfigure}
\begin{subfigure}[b]{.19\textwidth}
\includegraphics[width=\linewidth]{images/BLUT_output_00/6.jpg}
\end{subfigure}\\
\begin{subfigure}[b]{.19\textwidth}
\includegraphics[width=\linewidth]{images/BLUT_input_00/output2.jpg}
\end{subfigure}
\begin{subfigure}[b]{.19\textwidth}
\includegraphics[width=\linewidth]{images/BLUT_input_00/output3.jpg}
\end{subfigure}
\begin{subfigure}[b]{.19\textwidth}
\includegraphics[width=\linewidth]{images/BLUT_input_00/output4.jpg}
\end{subfigure}
\begin{subfigure}[b]{.19\textwidth}
\includegraphics[width=\linewidth]{images/BLUT_input_00/output5.jpg}
\end{subfigure}
\begin{subfigure}[b]{.19\textwidth}
\includegraphics[width=\linewidth]{images/BLUT_input_00/output6.jpg}
\end{subfigure}
\caption{\textbf{Top:} Output of BLUT~\cite{Wu:2011}. \textbf{Bottom:}
  Output of our algorithm on the same image 
  sequence. BLUT is able to track the fiducial till the third frame,
  but from the fourth frame onwards, BLUT looses track. In the first
  three frames, the size of the  bounding box is low, but in the fourth
  and fifth frame it is large, indicating a sudden forward movement
  of the quadcopter.} 
\label{fig:BLUT_compare_00}
\end{figure*}

\begin{figure*}
\begin{subfigure}[b]{.19\textwidth}
\includegraphics[width=\linewidth]{images/BLUT_output_01/11.jpg}
\end{subfigure}
\begin{subfigure}[b]{.19\textwidth}
\includegraphics[width=\linewidth]{images/BLUT_output_01/12.jpg}
\end{subfigure}
\begin{subfigure}[b]{.19\textwidth}
\includegraphics[width=\linewidth]{images/BLUT_output_01/13.jpg}
\end{subfigure}
\begin{subfigure}[b]{.19\textwidth}
\includegraphics[width=\linewidth]{images/BLUT_output_01/14.jpg}
\end{subfigure}
\begin{subfigure}[b]{.19\textwidth}
\includegraphics[width=\linewidth]{images/BLUT_output_01/15.jpg}
\end{subfigure}\\
\begin{subfigure}[b]{.19\textwidth}
\includegraphics[width=\linewidth]{images/BLUT_input_01/output11.jpg}
\end{subfigure}
\begin{subfigure}[b]{.19\textwidth}
\includegraphics[width=\linewidth]{images/BLUT_input_01/output12.jpg}
\end{subfigure}
\begin{subfigure}[b]{.19\textwidth}
\includegraphics[width=\linewidth]{images/BLUT_input_01/output13.jpg}
\end{subfigure}
\begin{subfigure}[b]{.19\textwidth}
\includegraphics[width=\linewidth]{images/BLUT_input_01/output14.jpg}
\end{subfigure}
\begin{subfigure}[b]{.19\textwidth}
\includegraphics[width=\linewidth]{images/BLUT_input_01/output15.jpg}
\end{subfigure}
\caption{{\bf Top:} Output of BLUT~\cite{Wu:2011} on a sequence containing
the ``01'' binary coded fiducial. {\bf Bottom:} Output of our
algorithm on the same image 
sequence. BLUT looses  track from the third frame onwards.}
\label{fig:BLUT_compare_01}
\end{figure*}

@@

In terms of numbers of fiducials, we are able to generate less markers
than ARTag. Many applications in robotics (e.g., quadcopter navigation)
may not require simultaneous use of a large number of fiducials.  Most
of the time, it is sufficient to have 4-6 different
fiducials. Nevertheless, we may be able to generate a larger number of
fiducials by using color backgrounds. This is an area of interest for
further investigation.
